---
title: "Ranking"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{V02-Ranking}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(consensus)
```

## Creating rankings

There are three

- ranking
- parse_ranking

### `ranking()`

|   | v | cname | decreasing | output |
|:---:|:--:|:--:|:--:|:--------:|
| Opt1 | x | -     | -          |  Ranks the numbers in `v` in ascending order giving them the defaults names $c_1, c_2, ..., c_n$. If `v` is a named vector...     |
| Opt2 | x | -     | x          |        |
| Opt3 | x | x     | -          |        |
| Opt4 | x | x     | x          |        |
|   | - | -     | x          | ERROR |
|   | - | x     | -          | ERROR |
|   | - | x     | x          | ERROR |


The function `ranking`

Objects of class ranking are represented with "≻". Given two candidates $c_1$ and
$c_2$ and the ranking $c_1 \succ c_2$ this must be read as "$c_1$ is better than $c_2$.
This is, $c_1$ is ranked in a better position than $c_2$.

There are three options

1. Candidates for the names are given
2. Candidates for the names are not give

```{r}
r1 <- c(3, 8, 1, 2, 5)
r1 <- ranking(r1)
r1
```

```{r}
r2 <- c(3, 8, 1, 2, 5)
names(r2) <- letters[1:5]
r2 <- ranking(r2)
r2
```

```{r}
r3 <- c(3, 8, 1, 2, 5)
names(r3) <- c(letters[1:4], letters[1])
r3 <- ranking(r3)
r3
```

```{r}
r4 <- c(3, 8, 1, 2, 5)
r4
```

```{r}
r5 <- c(3, 1, 1, 3, 3)
names(r5) <- letters[1:5]
r5
```

```{r}
as.numeric(r1)
is.ranking(r1)
as.numeric(r2)
is.ranking(r2)
as.numeric(r3)
is.ranking(r3)
as.numeric(r4)
is.ranking(r4)
as.numeric(r5)
is.ranking(r5)
```

### `parse_ranking`
## Errors

- The argument cnames must be a vector

## Checking that an object is a ranking

